Exploration

### 2018-03-14 exploration.Rmd
n0 instead of n_i

########
## predict distribution with fit models
########
#---- Truth: use estimated slopes to fill IPM matrix
U.f <- fill_IPM_matrices(n.cell, tmax, n_i, n, z.rng, buffer=0.5, discrete=1,
                         p.ipm, n_z, n_x, X, sdd, env.df, verbose=T)

#---- Realization: use estimated slopes to generate simulated data
S.f <- simulate_data(n.cell, tmax, n_i, z.rng, U.f$lo, U.f$hi, 
                     p.ipm, X, n_z, sdd, U.f$sdd.j, verbose=T)

>>>>

########
## predict distribution with fit models
########
#---- Truth: use estimated slopes to fill IPM matrix
U.f <- fill_IPM_matrices(n.cell, tmax, n0, n, z.rng, buffer=0.5, discrete=1,
                         p.ipm, n_z, n_x, X, sdd, env.df, verbose=T)

#---- Realization: use estimated slopes to generate simulated data
S.f <- simulate_data(n.cell, tmax, n0, z.rng, U.f$lo, U.f$hi, 
                     p.ipm, X, n_z, sdd, U.f$sdd.j, verbose=T)
